The Occurrence of Earth-Like Planets Around Other Stars

### 2014-11-28 paper/cover-letter.tex
Some bugfixes, as submitted to Science.

\begin{letter}{Dr. Leslie Sage\\The Macmillan Building\\4 Crinan Street\\London N1 9XW\\United Kingdom}

  \opening{Dear Dr. Sage:}

  Please find enclosed a submission for Nature Letters entitled ``The
  Occurrence of Earth-Like Planets Around Other Stars.''  The
  submission comprises approximately 1900 words of text and four
  figures (with captions).  We do not at this time have any extended
  sections, supplementary information or supporting manuscripts.  The
  requested brief paragraphs justifying publication in Nature and
  summarising the letter's appeal to a broad audience follow.

  \textbf{For the editor:} The quantity $\eta_\oplus$ is of broad
  scientific interest.  Its estimation is a chief goal of NASA's
  Kepler mission, but is complicated by the difficulty of detecting
  Earth-like planets about other stars.  In addition to constraining
  $\eta_\oplus$ using the complete Kepler data set, we have modelled
  the distribution of planet orbital periods and radii and find that
  it is well-fit by a single Gaussian component.  Our approach to
  reconstructing the period-radius distribution of planets is
  generally applicable to any survey with significant selection
  effects.

  \textbf{For the public:} We use the latest results from NASA's
  Kepler mission to count how many planets of roughly Earth's size
  orbit stars like the Sun in our galaxy at about the same distance
  from their host stars as Earth.  We find that about 4\% of stars
  have a planet the size of Earth in an Earth-like orbit; with about
  100 billion Sun-like stars in the galaxy, this means there are over
  4 billion Earth-sized planets in one year orbits in our galaxy!

>>>>

\begin{letter}{Dr. Maria Cruz\\Science/AAAS\\1200 New York Avenue NW\\Washington DC 20005\\United States}

  \opening{Dear Dr. Cruz:}

  Please find enclosed a report for submission to Science entitled
  ``The Occurrence of Earth-Like Planets Around Other Stars.''  The
  submission comprises approximately 2500 words of text, including
  four figures (with captions).

  The main result of our paper is a measurement of $\eta_\oplus$, the
  number density of Earth-sized planets in Earth-like orbits about
  stars similar to the sun.  Our measurement uses the complete data
  release from the final quarter of operation of the Kepler sattelite
  (Q17).  The quantity $\eta_\oplus$ is of broad scientific interest.
  Its estimation is a chief goal of NASA's Kepler mission, but is
  complicated by the difficulty of detecting Earth-like planets about
  other stars (i.e.\ selection effects); we deal with this difficulty
  using an innovative statistical technique that simultaneously fits
  the intrinsic distribution of planet periods and radii and a
  parameterised model of the Kepler selection function.  In addition
  to constraining $\eta_\oplus$, we have modelled the distribution of
  planet orbital periods and radii and find that it is well-fit by a
  single Gaussian component.  Our approach to reconstructing the
  intrinsic distribution of planet periods and radii is generally
  applicable to any survey with significant selection effects.

### 2014-11-28 paper/kepler-selection.tex
Some bugfixes, as submitted to Science.

A correlated log-normal distribution of planets in period and radius
would be a natural outcome of a stochastic planet formation process
that produced many correlated, fractional changes in planet sizes and
orbits.  As we shall see (Figure\ \ref{fig:selection}), this simple
model combined with the aforementioned selection function, provides a
good fit to the Kepler candidate distribution.  In our model, observed
planets populate the candidate $P$-$R$ plane with number density
\begin{equation}
  \label{eq:foreground-rate}
  \frac{dN_\mathrm{obs}}{d\ln P\, d\ln R} = \left[ \sum_\mathrm{stars}
    p_\mathrm{select}(P, R) \right] \Rpl N\left[ \mu, \Sigma
    \right]\left( \ln P, \ln R \right),
\end{equation}
where $\Rpl$, $\mu$, and $\Sigma$ are parameters of our model, with
$\Rpl$ the average number of planets per star, $\mu = \left[ \mu_P,
  \mu_R \right]$ the mean of $\ln P$ and $\ln R$, and $\Sigma = \left[
  \left[ \Sigma_{PP}, \Sigma_{PR} \right], \left[ \Sigma_{PR},
    \Sigma_{RR} \right]\right]$ the covariance matrix of $\ln P$ and
$\ln R$; $N\left[ \mu, \Sigma \right](x,y)$ is the normal distribution
Our model assumes that planets appear around their host stars in a
Poisson process; this is almost certainly wrong in
detail\cite{Weissbein2012}, but nevertheless provides a good fit to
the observed data (see Figure \ref{fig:selection}).

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{pars}
  \caption{\label{fig:eta-earth} \textbf{Posteriors on $\etaearth$ and
      $Rpl$ accounting for selection effects and false-positive
      detections.}  (Top) The inferred posterior density on $\etaearth
    = dN/d\ln P \, d\ln R \left( 1\, \textnormal{yr}, R_\oplus
    \right)$.  Vertical lines indicate the 90\% credible range.  We
    find $\etaearth = \earange$.  (Bottom) The inferred posterior on
    $\Rpl$, the number of planets per star with $P \lesssim 3
    \mathrm{yr}$ and $R \gtrsim 0.2 \REarth$.  Vertical lines indicate
    the 90\% credible range.  We find $\Rpl = \rplrange$.}
\end{figure}

>>>>

A correlated log-normal distribution of planets in period and radius
would be a natural outcome of a stochastic planet formation process
that produced many correlated, fractional changes in planet sizes and
orbits.  As we shall see (Figure\ \ref{fig:selection}), this simple
model combined with the aforementioned selection function provides a
good fit to the Kepler candidate distribution.  In our model, observed
planets populate the candidate $P$-$R$ plane with number density
\begin{equation}
  \label{eq:foreground-rate}
  \frac{dN_\mathrm{obs}}{d\ln P\, d\ln R} = \left[ \sum_\mathrm{stars}
    p_\mathrm{select}(P, R) \right] \Rpl N\left[ \mu, \Sigma
    \right]\left( \ln P, \ln R \right),
\end{equation}
where $\Rpl$, $\mu$, and $\Sigma$ are parameters of our model, with
$\Rpl$ the average number of planets per star, $\mu = \left[ \mu_P,
  \mu_R \right]$ the mean of $\ln P$ and $\ln R$, and $\Sigma = \left[
  \left[ \Sigma_{PP}, \Sigma_{PR} \right], \left[ \Sigma_{PR},
    \Sigma_{RR} \right]\right]$ the covariance matrix of $\ln P$ and
$\ln R$; $N\left[ \mu, \Sigma \right](x,y)$ is the normal
distribution.  Our model assumes that planets appear around their host
stars in a Poisson process; this is almost certainly wrong in
detail\cite{Weissbein2012}, but nevertheless provides a good fit to
the observed data (see Figure \ref{fig:selection}).

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{pars}
  \caption{\label{fig:eta-earth} \textbf{Posteriors on $\etaearth$ and
      $\Rpl$ accounting for selection effects and false-positive
      detections.}  (Top) The inferred posterior density on $\etaearth
    = dN/d\ln P \, d\ln R \left( 1\, \textnormal{yr}, R_\oplus
    \right)$.  Vertical lines indicate the 90\% credible range.  We
    find $\etaearth = \earange$.  (Bottom) The inferred posterior on
    $\Rpl$, the number of planets per star with $P \lesssim 3
    \mathrm{yr}$ and $R \gtrsim 0.2 \REarth$.  Vertical lines indicate
    the 90\% credible range.  We find $\Rpl = \rplrange$.}
\end{figure}
